Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. As expected in all case studies,
free energy, scalar order parameter, and strain combined 
are good topological indicators.

>>>>

Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
viscosity of the material gives a quantitative validation to support the statement. High 
shear-rate cases provide a range for critical shear rates where the structures break 
apart and undergo major topological changes. 
We further showed that
free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.
